|

### 2021-03-23 appendix/appendix.Rmd
appendix institution design and sparse matrix in rma.mv

```{r, size="footnotesize", error=F, warning=F, cache=T, echo = FALSE}
mod <- rma.mv(yi = coef,
              V = VAR,
              data = dat,
              method = "REML",
              random = ~ 1 | id_level1/id_level2, 
              mods = ~indepvar2+year+published+elecsys2+method,
              test = "knha",
              tdist = TRUE,
              subset = dat$depvar2=='ExpPC',
              slab = dat$authoryear)

@@

```{r, size="footnotesize", warning=F, cache=T, echo = FALSE}
mod <- rma.mv(yi = coef,
              V = VAR,
              data = fulldat,
              method = "REML",
              random = ~ 1 | id_level1/id_level2, 
              mods = ~indepvar2+year+published+elecsys2+method,
              test = "knha",
              tdist = TRUE,
              subset = fulldat$depvar2=='ExpPC',
              slab = fulldat$authoryear)

@@

```{r, size="footnotesize", warning=F, cache=T, echo = FALSE}
mod <- rma.mv(yi = coef,
              V = VAR,
              data = dat,
              method = "REML",
              random = ~ 1 | id_level1/id_level2, 
              mods = ~indepvar2+year+published+elecsys2+method,
              test = "knha",
              tdist = TRUE,
              subset = dat$depvar2=='logExpPC',
              slab = dat$authoryear)

@@

```{r, size="footnotesize", warning=F, cache=T, echo = FALSE}
mod <- rma.mv(yi = coef,
              V = VAR,
              data = fulldat,
              method = "REML",
              random = ~ 1 | id_level1/id_level2, 
              mods = ~indepvar2+year+published+elecsys2+method,
              test = "knha",
              tdist = TRUE,
              subset = fulldat$depvar2=='logExpPC',
              slab = fulldat$authoryear)

@@

```{r, size="footnotesize", warning=F, cache=T, echo = FALSE}
mod <- rma.mv(yi = coef,
              V = VAR,
              data = dat,
              method = "REML",
              random = ~ 1 | id_level1/id_level2, 
              mods = ~indepvar2+year+published+method,
              test = "knha",
              tdist = TRUE,
              subset = dat$depvar2=='PCTGDP',
              slab = dat$authoryear)

@@

```{r, size="footnotesize", warning=F, cache=T, echo = FALSE}
mod <- rma.mv(yi = coef,
              V = VAR,
              data = fulldat,
              method = "REML",
              random = ~ 1 | id_level1/id_level2, 
              mods = ~indepvar2+year+published+elecsys2+method,
              test = "knha",
              tdist = TRUE,
            subset = fulldat$depvar2=='PCTGDP',
            slab = fulldat$authoryear)
summary(mod)
```

@@

```{r, size="footnotesize", warning=F, cache=T, echo = FALSE}
mod <- rma.mv(yi = coef,
              V = VAR,
              data = dat,
              method = "REML",
              random = ~ 1 | id_level1/id_level2, 
              mods = ~depvar2+indepvar2+year+
                published+elecsys2+method,
              test = "knha",
              tdist = TRUE,
              slab = dat$authoryear)

@@

```{r, size="footnotesize", warning=F, cache=T, echo = FALSE}
mod <- rma.mv(yi = coef,
              V = VAR,
              data = fulldat,
              method = "REML",
              random = ~ 1 | id_level1/id_level2, 
              mods = ~depvar2+indepvar2+year+
                published+elecsys2+method,
              test = "knha",
              tdist = TRUE,
              slab = fulldat$authoryear)
summary(mod)
```
In the full model, we can see that:

>>>>

```{r, size="footnotesize", error=F, warning=F, cache=T, echo = FALSE}
mod <- rma.mv(yi = coef,
              V = VAR,
              data = dat,
              method = "REML",
              random = ~ 1 | id_level1/id_level2, 
              mods = ~indepvar2+year+published+elecsys2+method+instdesign,
              test = "knha",
              sparse = TRUE,
              tdist = TRUE,
              subset = dat$depvar2=='ExpPC',
              slab = dat$authoryear)

@@

```{r, size="footnotesize", warning=F, cache=T, echo = FALSE}
mod <- rma.mv(yi = coef,
              V = VAR,
              data = fulldat,
              method = "REML",
              random = ~ 1 | id_level1/id_level2, 
              mods = ~indepvar2+year+published+elecsys2+method+instdesign,
              test = "knha",
              tdist = TRUE,
              sparse = TRUE,
              subset = fulldat$depvar2=='ExpPC',
              slab = fulldat$authoryear)

@@

```{r, size="footnotesize", warning=F, cache=T, echo = FALSE}
mod <- rma.mv(yi = coef,
              V = VAR,
              data = dat,
              method = "REML",
              random = ~ 1 | id_level1/id_level2, 
              mods = ~indepvar2+year+published+elecsys2+method+instdesign,
              test = "knha",
              tdist = TRUE,
              sparse = TRUE,
              subset = dat$depvar2=='logExpPC',
              slab = dat$authoryear)

@@

```{r, size="footnotesize", warning=F, cache=T, echo = FALSE}
mod <- rma.mv(yi = coef,
              V = VAR,
              data = fulldat,
              method = "REML",
              random = ~ 1 | id_level1/id_level2, 
              mods = ~indepvar2+year+published+elecsys2+method+instdesign,
              test = "knha",
              tdist = TRUE,
              sparse = TRUE,
              subset = fulldat$depvar2=='logExpPC',
              slab = fulldat$authoryear)

@@

```{r, size="footnotesize", warning=F, cache=T, echo = FALSE}
mod <- rma.mv(yi = coef,
              V = VAR,
              data = dat,
              method = "REML",
              random = ~ 1 | id_level1/id_level2, 
              mods = ~indepvar2+year+published+elecsys2+method+instdesign,
              test = "knha",
              tdist = TRUE,
              sparse = TRUE,
              subset = dat$depvar2=='PCTGDP',
              slab = dat$authoryear)

@@

```{r, size="footnotesize", warning=F, cache=T, echo = FALSE}
mod <- rma.mv(yi = coef,
              V = VAR,
              data = fulldat,
              method = "REML",
              random = ~ 1 | id_level1/id_level2, 
              mods = ~indepvar2+year+published+elecsys2+method+instdesign,
              test = "knha",
              tdist = TRUE,
              sparse = TRUE,
            subset = fulldat$depvar2=='PCTGDP',
            slab = fulldat$authoryear)
summary(mod)
```

@@

```{r, size="footnotesize", warning=F, cache=T, echo = FALSE}
mod <- rma.mv(yi = coef,
              V = VAR,
              data = dat,
              method = "REML",
              random = ~ 1 | id_level1/id_level2, 
              mods = ~depvar2+indepvar2+year+published+elecsys2+method+instdesign,
              test = "knha",
              tdist = TRUE,
              sparse = TRUE,
              slab = dat$authoryear)

@@

```{r, size="footnotesize", warning=F, cache=T, echo = FALSE}
mod <- rma.mv(yi = coef,
              V = VAR,
              data = fulldat,
              method = "REML",
              random = ~ 1 | id_level1/id_level2, 
              mods = ~depvar2+indepvar2+year+published+elecsys2+method+instdesign,
              test = "knha",
              tdist = TRUE,
              sparse = TRUE,
              slab = fulldat$authoryear)
summary(mod)
```
In the full model, we can see that:
